---
title: "Cross Validation"
output: github_document
---

Load libraries that you will need:

```{r setup}
library(tidyverse)
library(viridis)

library(modelr)
library(mgcv)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Tools for CV
- add_predictions() and add_residuals
- rmse()
- crossv_mc()

## Simulate a dataset

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point()
```

Create splits by hand; plot; fit some models;

```{r}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df, by = "id")

train_df %>% arrange(id)
test_df

ggplot(train_df, aes(x = x, y = y)) +
  geom_point() +
  geom_point(data = test_df, color = "red")
```

Fit my models:

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

plot the results

```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred))

train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred))

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred))
```

Quantify the results

rmse = root mean squared error

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

## Cross Validation iteratively

Use 'modelr::crossv_mc'.
- mc refers to Monte Carlo
- partition the nonlinear df 100 times
- defaults to 20% in the testing data set

```{r}
cv_df =
  crossv_mc(nonlin_df, 100)

cv_df %>% pull(train) %>% .[[1]] %>% as_tibble()
```

Now we want to convert everything to tibbles instead of 'resamples'

```{r}
cv_df =
  crossv_mc(nonlin_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

Let's fit some models...

```{r}
cv_df %>% 
  mutate(
    linear_mod = map(.x = train, ~lm(y ~ x, data = .x))
  ) %>%
  mutate(
    rmse_linear = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y))
  )
```

Let's fit some additional models

```{r}
cv_df = cv_df %>% 
  mutate(
    linear_mod = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_mod = map(.x = train, ~gam(y ~ s(x), data = .x)),
    wiggly_mod = map(.x = train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))
  ) %>%
  mutate(
    rmse_linear = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(.x = wiggly_mod, .y = test, ~rmse(model = .x, data = .y))
  )
```

Look at the output
Ideally using a boxplot

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    rmse_linear:rmse_wiggly,
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
```

Boxplots help us understand across 100 testing and training datasets, which one had the lowest rmse.

