---
title: "Linear Models"
output: github_document
---

Load libraries that you will need:

```{r setup}
library(tidyverse)
library(p8105.datasets)
library(viridis)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Notes
lm is used for linear models
glm is used for generalized linear models (e.g. logistic regression)


## Load the NYC airbnb dataset

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

Visualization...

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point()
```

Note that assumption of normality is violated based on the scatterplot above, because there's greater variability in price at higher star ratings. But generally we see that as star rating goes up, prices go up

Let's fit a linear model...

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

Let's take a look at this...

```{r}
fit
summary(fit)
summary(fit)$coef

fit %>% broom::tidy()
```

If you want to present output...

```{r}
fit %>%
  broom::tidy() %>% 
  mutate(term = str_replace(term, "borough", "Borough: ")) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

## Diagnostics

Use this code to add residuals to your data frame.
It's possible to add residuals from several different models.

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) + 
  geom_point()

modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = resid)) + 
  geom_density() + 
  xlim(-200, 200)
```
This plot again shows that distributions are skewed, though means are probably centered around zero.

## Hypothesis testing - see course website

## Interactions? Nesting?

Let's try to fit a different model

```{r}
fit = lm(price ~ stars + room_type, data = nyc_airbnb)

broom::tidy(fit)

fit = lm(price ~ stars * borough + room_type * borough, data = nyc_airbnb)

broom::tidy(fit)
```

Let's try nesting...

```{r}
nyc_airbnb %>% 
  relocate(borough) %>% 
  nest(data = price:room_type) %>% 
  mutate(
    lm_fits = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    lm_results = map(lm_fits, broom::tidy)
  ) %>% 
  select(borough, lm_results) %>% 
  unnest(lm_results) %>% 
  filter(term == "stars")
```

Look at neighborhoods in Manhattan...

```{r}
manhattan_lm_results_df = nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  select(-borough) %>% 
  relocate(neighborhood) %>% 
  nest(data = price:room_type) %>% 
  mutate(
    lm_fits = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    lm_results = map(lm_fits, broom::tidy)
  ) %>% 
  select(neighborhood, lm_results) %>% 
  unnest(lm_results)

manhattan_lm_results_df %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + 
  geom_density()
```
Density plot shows that across neighborhoods in Manhattan, increasing stars does not impact price, adjusting for room type, since the most estimates are around 0.

```{r}
manhattan_lm_results_df %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) +
  geom_point() + 
  facet_grid(~term) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
In every neighborhood in Manhattan, we have a coefficient for price on room type, adjusting for stars. For Battery park, going from an entire home to a private room costs about $100 less per night. This is relatively stable across almost all neighborhoods in Manhattan. Also the same from an entire home to a shared room.
